### 2017-03-13 thesis/results/results2.tex
Need to add linear model prediction scatter plots - tmp commit

	\caption{Description of the linear models used to predict the CR obesity metagene in \gls{nzbc} data set}

@@

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the CR obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{1}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & 0.081\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
				\end{footnotesize}
			\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\noindent
Lastly, since only the ``consistent'' pathway metagenes were picked from all of the available pathway metagene scores, linear models were constructed with all of the pathway metagenes in a step wise fashion.
Step wise construction of a linear model is where the variables for a model are selected computationally depending on the contribution of the variable to the resuting linear model, and thus contains only the variables that ``matter'' to the linear model.
Sample \gls{bmi}, \gls{bmi} status and all of the pathway metagene scores were used to generate the step wise linear model for each of the obesity metagenes.
The linear models that resulted from the step wise selection of the variables were summarised in \cref{app:b}.

>>>>

	\caption{Description of the linear models used to predict the Cr obesity metagene in \gls{nzbc} data set}

@@

\begin{table}[htpb]
	\centering
	\caption{Description of the linear models used to predict the Cr obesity metagene in \gls{nzbc} data set, using only the sample \gls{bmi}, \gls{bmi} status and \gls{pr} pathway metagene scores}
	\label{tab:lm_pr_only}
	\begin{threeparttable}
			\begin{tabular}{llr{\bfseries}S}
				Linear Model & Variables & Estimate & {P-value}\\
				\hline
				\hline
				\rule{0pt}{2.25ex}\gls{pr} only                            & \gls{pr}   & 0.477  & {\bfseries \num{6.06d-7}}\tnote{1}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} and \gls{pr}                   & \gls{bmi}  & -0.002 & 0.586\\
                                                                           & \gls{pr}   & 0.478  & {\bfseries \num{6.35d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi} status and \gls{pr}            & Obese      & -0.085 & 0.176\\
                                                                           & Overweight & -0.011 & 0.875\\
                                                                           & \gls{pr}   & 0.471  & {\bfseries \num{8.25d-7}}\\
				\hline
				\rule{0pt}{2.25ex}\gls{bmi}, \gls{bmi} status and \gls{pr} & \gls{bmi}  & 0.007  & 0.237\\
                                                                           & Obese      & -0.188 & 0.081\\
                                                                           & Overweight & -0.049 & 0.516\\
                                                                           & \gls{pr}   & 0.459  & {\bfseries \num{1.54d-6}}\\
				\hline
				\hline
			\end{tabular}
			\begin{tablenotes}
				\begin{footnotesize}
					\item [1] All values in bold are statistically significant (p \textless{} 0.05).
				\end{footnotesize}
			\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\noindent
Lastly, since only the ``consistent'' pathway metagenes were picked from all of the available pathway metagene scores, linear models were constructed with all of the pathway metagenes in a step wise fashion.
Step wise construction of a linear model is where the variables for a model are selected computationally depending on the contribution of the variable to the resuting linear model, and thus contains only the variables that ``matter'' to the linear model.
Sample \gls{bmi}, \gls{bmi} status and all of the pathway metagene scores were used to generate the step wise linear model for each of the obesity metagenes.
The linear models that resulted from the step wise selection of the variables were summarised in \cref{tab:stepwise_model}.

\begin{longtable}{llr{\bfseries}S}
	\caption{Description of the step wise linear models used to predict all of the obesity metagenes in \gls{nzbc} data set}
	\label{tab:stepwise_model}\\
		Obesity metagene & Variables used in the model & Estimate & {P-value}\\
	\endfirsthead
	\multicolumn{4}{c}{\tablename\ \thetable{}\ (continued)}\\
	\endhead
		Cr         & Akt         & -0.3415   & \bfseries \num{4.43d-8}\\
				   & \gls{egfr}  & 0.33852   & \bfseries \num{1.94d-05}\\
				   & \gls{er}    & -0.20237  & \bfseries 0.00419\\
				   & \gls{ifny}  & 0.12233   & 0.08700\\
				   & \gls{pr}    & -0.33920  & \bfseries \num{2.09d-5}\\
				   & Ras         & -0.22611  & \bfseries 0.00193\\
				   & Src         & -0.11452  & 0.08177\\
				   & \gls{tgfb}  & 0.55638   & \bfseries \textless{} \num{2d-16}\\
				   & \gls{tnfa}  & -0.25501  & \bfseries 0.00616\\
		CrOl       & Overweight  & 0.040918  & 0.074865\\
				   & Obese       & -0.006381 & 0.756121\\
				   & Akt         & -0.356713 & \bfseries \num{1.89d-07}\\
				   & E2F1        & 0.160229  & \bfseries 0.005411\\
				   & \gls{egfr}  & 0.148618  & 0.062683\\
				   & p53         & 0.336552  & \bfseries \num{4.35d-05}\\
				   & \gls{pr}    & -0.225423 & \bfseries 0.000639\\
				   & Src         & -0.428758 & \bfseries \num{5.85d-10}\\
				   & \gls{stat3} & -0.124118 & \bfseries 0.009658\\
		Res        & Akt         & 0.24613   & \bfseries 0.000289\\
				   & \gls{egfr}  & -0.46827  & \bfseries \num{2.16d-05}\\
				   & \gls{er}    & 0.18400   & 0.061446\\
				   & \gls{her2}  & 0.13835   & 0.118228\\
				   & \gls{ifny}  & -0.21019  & \bfseries 0.044084\\
				   & \gls{pr}    & 0.41195   & \bfseries 0.000300\\
				   & Ras         & 0.26506   & \bfseries 0.010465\\
				   & \gls{tgfb}  & -0.58075  & \bfseries \num{7.64d-11}\\
				   & \gls{tnfa}  & 0.42200   & \bfseries 0.001834\\
		ResOl      & Akt         & -0.33596  & \bfseries 0.000294\\
				   & \gls{bcat}  & -0.19866  & 0.138953\\
				   & E2F1        & 0.36059   & \bfseries 0.009325\\
				   & \gls{egfr}  & 0.23421   & 0.056865\\
				   & \gls{her2}  & -0.13652  & 0.121689\\
				   & p53         & 0.38746   & \bfseries 0.000519\\
				   & \gls{pi3k}  & -0.21881  & 0.148676\\
				   & \gls{pr}    & -0.32228  & \bfseries 0.001656\\
				   & Ras         & -0.28984  & \bfseries 0.033975\\
				   & Src         & -0.40779  & \bfseries \num{5.26d-06}\\
				   & \gls{stat3} & -0.11452  & 0.125609\\
				   & \gls{tnfa}  & -0.11442  & 0.117023\\
		Ca         & Akt         & -0.26243  & \bfseries \num{7.04d-06}\\
				   & \gls{egfr}  & 0.36305   & \bfseries 0.000139\\
				   & \gls{er}    & -0.18614  & \bfseries 0.030771\\
				   & \gls{ifny}  & 0.22118   & \bfseries 0.013034\\
				   & \gls{pr}    & -0.42911  & \bfseries \num{1.07d-05}\\
				   & Ras         & -0.28124  & \bfseries 0.000898\\
				   & \gls{tgfb}  & 0.76139   & \bfseries \textless{} \num{2d-16}\\
				   & \gls{tnfa}  & -0.33200  & \bfseries 0.003919\\
		CaOl       & Overweight  & 0.07613   & \bfseries 0.006875\\
				   & Obese       & 0.01408   & 0.564622\\
				   & Akt         & -0.44727  & \bfseries \num{2.43d-07}\\
				   & \gls{bcat}  & -0.13463  & 0.140261\\
				   & E2F1        & 0.33864   & \bfseries 0.001249\\
				   & p53         & 0.28777   & \bfseries 0.000996\\
				   & \gls{pr}    & -0.28255  & \bfseries \num{2.18d-05}\\
				   & Src         & -0.44149  & \bfseries \num{2.02d-08}\\
				   & \gls{tnfa}  & -0.14215  & \bfseries 0.013897\\
		CaRes      & \gls{bcat}  & 0.26899   & 0.05238  \\
				   & E2F1        & -0.22115  & 0.08848  \\
				   & \gls{egfr}  & 0.44400   & \bfseries \num{6.67d-05 }\\
				   & \gls{her2}  & -0.20304  & \bfseries 0.04615  \\
				   & \gls{ifny}  & 0.32874   & \bfseries 0.00574  \\
				   & \gls{pr}    & -0.28764  & \bfseries 0.00104  \\
				   & Src         & -0.17989  & 0.05404  \\
				   & \gls{tgfb}  & 0.52898   & \bfseries \num{2.15d-06 }\\
				   & \gls{tnfa}  & -0.38677  & \bfseries 0.00564  \\
		CaResOl    & \gls{bmi}   & 0.004314  & 0.108546\\
				   & Overweight  & 0.033086  & 0.306390\\
				   & Obese       & -0.062257 & 0.175776\\
				   & Akt         & -0.309706 & \bfseries 0.000339\\
				   & \gls{bcat}  & -0.198165 & 0.140502\\
				   & E2F1        & 0.270471  & \bfseries 0.011450\\
				   & \gls{egfr}  & 0.171219  & 0.113691\\
				   & Myc         & 0.152007  & 0.056987\\
				   & p53         & 0.294895  & \bfseries 0.003734\\
				   & \gls{pr}    & -0.230896 & \bfseries 0.000823\\
				   & Ras         & -0.270824 & \bfseries 0.044788\\
				   & Src         & -0.512567 & \bfseries \num{2.72d-08}\\
				   & \gls{tnfa}  & -0.103302 & 0.083449\\
		Or         & \gls{bmi}   & 0.002696  & 0.14407\\
				   & Overweight  & 0.010522  & 0.62856\\
				   & Obese       & -0.061020 & 0.05542\\
				   & Akt         & -0.238412 & \bfseries \num{4.93d-05}\\
				   & E2F1        & 0.185085  & \bfseries 0.02754\\
				   & \gls{egfr}  & 0.147219  & 0.07423\\
				   & \gls{her2}  & -0.086804 & 0.14070\\
				   & p53         & 0.416414  & \bfseries \num{5.83d-08}\\
				   & \gls{pi3k}  & -0.216179 & \bfseries 0.03528\\
				   & \gls{pr}    & -0.199097 & \bfseries 0.00253\\
				   & Ras         & -0.200544 & \bfseries 0.00898\\
				   & Src         & -0.543834 & \bfseries \num{2.10d-15}\\
				   & \gls{stat3} & -0.093363 & \bfseries 0.02749\\
		FM         & \gls{bmi}   & 0.011093  & \bfseries 0.036229\\
				   & Overweight  & -0.153753 & \bfseries 0.014277\\
				   & Obese       & -0.212483 & \bfseries 0.017378\\
				   & p53         & 0.460800  & \bfseries 0.002512\\
				   & \gls{pi3k}  & -0.426246 & \bfseries 0.000118\\
				   & \gls{pr}    & -0.373119 & \bfseries 0.020737\\
				   & \gls{stat3} & 0.248745  & \bfseries 0.019073\\
				   & \gls{tgfb}  & 0.152925  & 0.128933\\
	\end{longtable}
